hormones

### 2019-10-11 analysis/07_hormones.Rmd
now with outlier color

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment, color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x =  element_blank(),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) 
}

>>>>

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment, color = sex)) +
    geom_boxplot(aes(outlier.colour = treatment)) +
    theme(axis.text.x =  element_blank(),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) 
}
